State and Parameter Estimation for Spatio-Temporal Neural Fields

### 2010-06-16 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
mean bias of xi and theta0

The distribution of the estimated parameters is shown in Figure~\ref{fig:Parameters}. The mean parameter estimates and the corresponding standard deviations are given in Table~\ref{tab:Parameters estimates}. The estimates for $\xi$, where $\xi=1-\zeta T_s $ and $\zeta$ is the reciprocal of the synaptic time constant, are close to the actual values, however show a small bias (with a mean bias of 2.7~\%). The estimates of the connectivity kernel parameters ($\theta_0$, $\theta_1$, $\theta_2$) form distributions that are approximately Gaussian. The mean parameter estimates are in good accordance with the actual values, with biases of 2.778, 7.138 and 10.2~\% for $\theta_0$, $\theta_1$ and $\theta_2$ respectively. The ratios of the estimates ($\hat\theta_0/\hat\theta_1$ and $\hat\theta_0/\hat\theta_2$) are shown in Figure~\ref{fig:ParametersRatio}. The distribution of estimates for $\hat\theta_0/\hat\theta_1$ are relativity tighter\parham{(it's 0.0812 (a bit tighter) and 3.757 respectively)}, though indicate a bias... This indicates the balance of excitation and inhibition can be estimated more accurately than the individual parameters.

>>>>

The distribution of the estimated parameters is shown in Figure~\ref{fig:Parameters}. The mean parameter estimates and the corresponding standard deviations are given in Table~\ref{tab:Parameters estimates}. The estimates for $\xi$, where $\xi=1-\zeta T_s $ and $\zeta$ is the reciprocal of the synaptic time constant, are close to the actual values, however show a small bias (with a mean bias of 2.778~\%). The estimates of the connectivity kernel parameters ($\theta_0$, $\theta_1$, $\theta_2$) form distributions that are approximately Gaussian. The mean parameter estimates are in good accordance with the actual values, with biases of 2.95, 7.138 and 10.2~\% for $\theta_0$, $\theta_1$ and $\theta_2$ respectively. The ratios of the estimates ($\hat\theta_0/\hat\theta_1$ and $\hat\theta_0/\hat\theta_2$) are shown in Figure~\ref{fig:ParametersRatio}. The distribution of estimates for $\hat\theta_0/\hat\theta_1$ are relativity tighter\parham{(it's 0.0812 (a bit tighter) and 3.757 respectively)}, though indicate a bias... This indicates the balance of excitation and inhibition can be estimated more accurately than the individual parameters.
